### 2018-10-10 Chapters/Chapter3.tex
Fix

\begin{equation}
\hat{H}'(t) = \hat{U}^\dagger (t) \hat{H}(t) \hat{U}(t) - i\hat{U}^\dagger(t) d_t \hat{U}(t)
\end{equation}

@@

Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$. Using the Baker–Campbell–Hausdorff expansion we can write the transformed Hamiltonian as:

\begin{equation}
\label{Perturbation}
\hat{H}'(t) = \hat{H}(t) + \sum_{n=1}^\infty \frac{1}{n!} \left[i\hat{S}(t), \dots, \left[ i\hat{S}(t), \hat{H}(t) \right]\dots \right] - d_t \hat{S}(t)
\end{equation}

Now, starting from order zero and for each order we will determine $i\hat{S}^{(\nu)}(t)$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number. To zeroth order in $\eta$ we have $\hat{H}'^{(0)}= U\hat{D}$ and $i\hat{S}^{(0)}(t)=0$. In first order we obtain:

\begin{equation}
\label{1stO}
\hat{H}'^{(1)}(t) = -\hat{T}(t) + \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] - d_t\hat{S}^{(1)}(t)
\end{equation}

@@

\begin{equation}
\hat{H}'^{(2)}(t) = \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
\end{equation}

@@

For $\bs{D}_{ij}(t)$ this is:

@@

\begin{section}{Identities}

Let $Z(t)$ be an operator dependent on the parameter $t$. Then:

@@

\begin{equation}
d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
\end{equation}

>>>>

\begin{equation}
\hat{H}'(t) = e^{i\hat{S}(t)} \hat{H}(t) e^{-i\hat{S}(t)} - e^{i\hat{S}(t)} id_t e^{-i\hat{S}(t)}
\end{equation}

@@

Where $\hat{T}_d(t)$ changes the double occupancy number by $d$, for example $\hat{T}_1(t) = \hat{P}_1 \hat{T}(t) \hat{P}_0$. Now we can use the identity:

\begin{equation}
id_t e^{-i\hat{S}(t)} = \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))e^{-i\hat{S}(t)}
\end{equation}

Derived in appendix \ref{AP3B}, where $\text{ad}_A(B) = [A,B]$. To rewrite the transformed Hamiltonian as:

\begin{equation}
\hat{H}'(t) = e^{i\hat{S}(t)} \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right) e^{-i\hat{S}(t)}
\end{equation}

Using the Baker–Campbell–Hausdorff expansion we can write the transformed Hamiltonian as:

\begin{equation}
\label{PertFull}
\hat{H}'(t) = \sum_m \frac{1}{m!} \text{ad}_{i\hat{S}(t)}^m \left( \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) \right)
\end{equation}

Now, in this expression we have to expand $\hat{S}(t) = \sum_\nu \eta^\nu \hat{S}^{(\nu)}(t)$ and $\hat{H}'(t) = \sum_\nu \eta^\nu \hat{H}'^{(\nu)}(t)$ and determine $\hat{S}^{(\nu)}(t)$ iteratively in $\nu$ so that $\hat{H}'^{(\nu)}(t)$ is diagonal in the doublon number. Notice that we do not expand $\hat{H}(t)$ as an infinite series since $\hat{H}(t) = -\eta \hat{T}(t) + U\hat{D}$. Now, notice also that if we take $i\hat{S}^{(0)}(t)=0$ in \ref{PertFull}, then, to zeroth order in $\eta$ only terms in $m=0$ and $n=0$ contribute obtaining:

\begin{equation}
\hat{H}'^{(0)}(t) = U\hat{D}
\end{equation}

Which is indeed diagonal in the doublon number, and therefore we can take $i\hat{S}^{(0)}(t)=0$. With this equating terms of the same order in \ref{PertFull} is greatly simplified, since terms with high $m,n$ will correspond to terms with high $\eta$. Since we are only interested in orders up to second order, we can truncate \ref{PertFull} up to $m=2$:

\begin{align}
\label{PertTrunc}
\hat{H}'(t) &=  \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) + [i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t))] + \nonumber \\
&+ \frac{1}{2} [i\hat{S}(t),[i\hat{S}(t), \hat{H}(t) - \sum_n \frac{1}{(n+1)!}\text{ad}_{-i\hat{S}(t)}^n (d_t \hat{S}(t)) ]]
\end{align}

This equation holds up to order $\eta^2$. In first order we obtain:

\begin{equation}
\label{1stO}
\hat{H}'^{(1)}(t) = -\hat{T}(t) - d_t\hat{S}^{(1)}(t) + \left[ i\hat{S}^{(1)}(t), U\hat{D} \right]
\end{equation}

@@

\begin{align}
\hat{H}'^{(2)}(t) &= - d_t\hat{S}^{(2)}(t) - \frac{1}{2}\left[-i\hat{S}^{(1)}(t), d_t\hat{S}^{(1)}(t) \right] + \left[i\hat{S}^{(1)}(t), -\hat{T}(t)-\frac{1}{2}d_t\hat{S}^{(1)}(t) \right] +\nonumber \\
&+ \left[i\hat{S}^{(2)}(t), U\hat{D} \right] + \frac{1}{2} \left[i\hat{S}^{(1)}(t), \left[i\hat{S}^{(1)}(t), U\hat{D} \right] \right] = \nonumber \\
&= \left[i\hat{S}^{(2)}(t), U \hat{D} \right] - \left[ i\hat{S}^{(1)}(t), \hat{T}(t) \right] + \frac{1}{2}\left[ i\hat{S}^{(1)}(t), \left[ i\hat{S}^{(1)}(t), U\hat{D} \right] \right] - d_t\hat{S}^{(2)}(t)
\end{align}

@@

Kinetic hopping and the Rashba spin orbit are both NN hopping processes, so they are both renormalized in the same way by the laser field \cite{Stepanov2017}.
For $\bs{D}_{ij}(t)$ this is:

@@

\begin{section}{Identities}
\label{AP3B}
Let $Z(t)$ be an operator dependent on the parameter $t$. Then:

@@

\begin{equation}
\label{SneidersID}
d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \text{ad}_Z ^n \left(\frac{\partial Z}{\partial t}\right) e^Z
\end{equation}

Where $\text{ad}_A(B) = [A,B]$.
